Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-22 IJCAR2020/absoluteness.tex
ediciones menores al paper

The version of \isatt{ZF-Constructible} we present weakens the
assumptions of [many / a dozen / several] absoluteness theorems to that
of a nonempty transitive class.
%
\begin{framed}
  New absoluteness results on powersets --- for \isatt{Least} and
  \isatt{Vset} see Section~\ref{sec:axioms-replacement-choice}
\end{framed}

>>>>

The version of \isatt{ZF-Constructible} we present weakens the
assumptions of many absoluteness theorems to that
of a nonempty transitive class; also there are some stronger results
such as the relativization of powersets.

### 2020-01-22 IJCAR2020/intro.tex
ediciones menores al paper

In the course of our work we find it useful to develop Isar methods to
automate repetitive tasks. Part of the interface with Paulson's
library consisted in constructing formulas for each relativized
concept; Isar already has a method (\texttt{schematic\_goal}) which can
synthesize terms for unbound schematic variables in theorems. The
synthesized term, however, is not available outside the theorem; we
introduced a method that creates a definition from a schematic
goal. The second method is concerned with renaming of formulas: we
improved our small library of bounded renamings with a method that
given the source and target environments figures out the renaming
function and produces the relevant lemmas about it.

>>>>

In the course of our work we found it useful to develop Isar methods to
automate repetitive tasks. Part of the interface with Paulson's
library consisted in constructing formulas for each relativized
concept; and actually Isabelle's Simplifier can
synthesize terms for unbound schematic variables in theorems. The
synthesized term, however, is not available outside the theorem; we
introduced a method that creates a definition from a schematic
goal. The second method is concerned with renaming of formulas: we
improved our small library of bounded renamings with a method that
given the source and target environments figures out the renaming
function and produces the relevant lemmas about it.
